Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-18 manuscript/draft.Rmd
Editorial changes to abstract

Biodiversity forecasts are important for conservation, management, and
evaluating how well current models characterize natural systems. While
biodiversity forecasts are common, there is little information available on how
well these forecasts work. Most biodiversity forecasts are not evaluated in
terms of their ability to predict future diversity, fail to account for
uncertainty, and do not use time-series data that captures the actual dynamics
being studied. We compiled a list of ten best practices for forecasting
biodiversity, and used hindcasting to evaluate six different modeling approaches
for predicting breeding bird species richness. Each method was evaluated at `r
numbers$N_predict_sites` sites distributed throughout the continental United
States. Forecasts were evaluated for up to a decade after the final training
observations. While each model could explain most of the variance in richness,
none of them consistently outperformed a baseline model that simply predicted
constant richness at each site. In particular, we found no evidence that current
methods (such as species distribution models) can successfully turn spatial data
into useful temporal predictions about biodiversity. This result may call into
question the validity of many high-profile forecasts from the last 15 years.
Most of the best practices implemented in this study (e.g., evaluating
confidence intervals as well as point estimates) directly influence the outcome
of the forecasts; some even led to large changes in the relative performance of
different modeling approaches. To facilitate the rapid improvement of
biodiversity forecasts, we emphasize the value of specific best practices in
making and evaluating different forecasting methods.

>>>>

Biodiversity forecasts are important for conservation, management, and
evaluating how well current models characterize natural systems. While the
number of forecasts for biodiversity are increasing, there is little information
available on how well these forecasts work. Most biodiversity forecasts are not
evaluated to determine how well they predict future diversity, fail to account
for uncertainty, and do not use time-series data that captures the actual
dynamics being studied. We addressed these limitations by using best practices
to explore our ability to forecast the species richness of breeding birds in
North America. We used hindcasting to evaluate six different modeling approaches
for predicting richness. Hindcasts for each method were evaluated annually for a
decade at `r numbers$N_predict_sites` sites distributed throughout the
continental United States. While each model could explain most of the variance
in richness, none of them consistently outperformed a baseline model that
predicted constant richness at each site. In particular, we found no evidence
that current methods (such as species distribution models) can successfully turn
spatial data into useful temporal predictions about biodiversity at decadale
time-scales. The best practices implemented in this study directly influence the
forecasts, the relative performance of different modeling approaches, and the
conclusions about the current state of biodiversity forecasting . To facilitate
the rapid improvement of biodiversity forecasts, we emphasize the value of
specific best practices in making forecasts and evaluating forecasting methods.
